What Does Reproducible Research Mean for Plant Pathology?

### 2016-09-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Remove redundant files, add links in README.Rmd, fix links in manuscript

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide 
[http://adamhsparks.github.io/MICCORDEA/](models, data and code) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide 
[http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/](models, data and code)
necessary to replicate model development and the subsequent the study on the effects
of climate change on potato late blight.
* Other examples from plant pathology providing e-Xtras or supplemental material

>>>>

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects
of climate change on potato late blight.
* Other examples from plant pathology providing e-Xtras or supplemental material
